---
title: "Monthly Update"
author:
date:
output:
  powerpoint_presentation:
  #  reference_doc: report_template.pptx
---

```{r setup, include=FALSE}
# Libraries
library(knitr)
library(flextable)
library(tidyverse)
library(lubridate)

# Knitr options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE,
                      dpi = 300)
```

## Refresher

- What is the NeoTree?
    - An electronic medical record/decision support tool
    - Gradual introduction from 12th November 2018
- Currently used in the NNU for admissions and discharges
    - Hard copies printable in both NNU and labour ward
- Used for feeding back blood culture results directly to the NNU

## Progress to end `r format(ymd(analysis_month, truncated = 1), "%B %Y")`

```{r,}
df1 %>%
  flextable %>%
  set_header_labels(EventType = "Event", Number = "Count") %>%
  colformat_num(j = "Number", digits = 0) %>%
  theme_booktabs(fontsize = 20) %>%
  autofit
```

## `r format(ymd(analysis_month, truncated = 1), "%B %Y")` statistics

```{r}
df2 %>%
  flextable %>%
  set_header_labels(EventType = "Event", Number = "Count") %>%
  colformat_num(j = "Number", i = 1:4, digits = 0) %>%
  colformat_num(j = "Number", i = 5, digits = 2) %>%
  theme_booktabs(fontsize = 20) %>%
  autofit
```

##

```{r}
#Admission each month
plot1
```

##

```{r}
#Discharges and deaths each month
plot2
```

##

```{r}
plot3
```

##

```{r}
plot4
```

##

```{r}
plot5
```

##

```{r}
plot6
```

##

```{r}
plot7
```

##

```{r}
plot8
```

##

```{r}
plot9
```

##

```{r}
plot10
```

##

```{r}
plot11
```

##

```{r}
plot12
```

## Questions or suggestions?





