---
title: Monthly Report for Sister in Charge
author: Prepared by the NeoTree Team
date:
output: html_document
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r setup, include=FALSE}
# Libraries
library(knitr)
library(kableExtra)
library(tidyverse)
library(lubridate)

# Knitr options
knitr::opts_chunk$set(echo = FALSE)
```

<div style="margin-top: 20px; margin-bottom:50px; font-size:16pt">

This report is for the month of `r format(ymd(analysis_month, truncated = 1), "%B %Y")`.

</div>

<div style="margin-bottom:50px;">

# Summary counts for this month

```{r}
df3 %>%
  knitr::kable(col.names = c("Event", "Count")) %>%
  kable_styling(latex_options = "striped", position = "left") %>%
  row_spec(0, bold = T)
```

</div>

<div style="margin-bottom:50px;">

# Causes of death this month

```{r}
df5 %>%
  knitr::kable(col.names = c("Cause of Death", "Number")) %>%
  kable_styling(bootstrap_options = "striped", position = "left") %>%
  row_spec(0, bold = T)
```

*Note:* If 'Other' is a cause of death this month, the text entered by the healthcare worker will be shown below.

<br>

```{r}
if (df5$Number[[9]] > 0) {
  new.discharge.df %>%
               select(Discharge.CauseDeathOther) %>%
               filter(!is.na(Discharge.CauseDeathOther),
                      Discharge.CauseDeathOther != "",
                      grepl(analysis_month, new.discharge.df$disDiedDateTime)) %>%
    knitr::kable(col.names = "Cause of Death if 'Other'") %>%
    kable_styling(bootstrap_options = "striped", position = "left") %>%
    row_spec(0, bold = T)
} else {
  cat("'Other' is not a cause of death this month.")
}
```

</div>

<div style="margin-bottom:50px">

# Top 5 discharge diagnoses this month

```{r}
df4a %>%
  knitr::kable(col.names = c("Discharge Diagnosis", "Number")) %>%
  kable_styling(bootstrap_options = "striped", position = "left") %>%
  row_spec(0, bold = T)
```

*Note:* If 'Other' appears in the top 5 diagnoses, the text entered by the healthcare worker will be shown below.

<br>

```{r}
if (any(grepl("Other", df4a[[1]]))) {
  new.discharge.df %>%
               select(Discharge.DIAGDIS1OTH) %>%
               filter(!is.na(Discharge.DIAGDIS1OTH),
                      grepl(analysis_month, new.discharge.df$disDiedDateTime)) %>%
    knitr::kable(col.names = "Discharge Diagnosis if 'Other'") %>%
    kable_styling(bootstrap_options = "striped", position = "left") %>%
    row_spec(0, bold = T)
} else {
  cat("'Other' is not in the top 5 discharge diagnoses this month.")
}
```

</div>